CLT Results

### 2022-04-19 analysis/clt_irt_analysis.Rmd
add more data
add joyplot

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(tidyboot)
library(brms)
library(readxl)
library(ggthemes)
library(geomtextpath)
library(coda)

@@

>>>>

```{r setup, include=FALSE}
library(tidyverse)
library(ggpubr)
library(tidyboot)
library(brms)
library(readxl)
library(ggthemes)
library(geomtextpath)
library(coda)
library(ggridges)

@@

```{r}
eta_joy <- as_draws_df(irt3)%>%
  select(b_eta_Intercept, starts_with("r_targetWord__eta"))%>%
  mutate(iter = 1:n()) %>%
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(name = str_remove(name, pattern = "r_targetWord__eta"),
         name = str_remove(name, pattern = "\\,Intercept"),
         name = str_remove_all(name, pattern = "\\[|\\]"))%>%
  mutate(val = b_eta_Intercept + value)%>%
  select(-b_eta_Intercept, -value)%>%
  mutate(nlpar = "Easiness")%>%
  filter(val < 8)

alpha_joy <- as_draws_df(irt3)%>%
  select(b_logalpha_Intercept, starts_with("r_targetWord__logalpha"))%>%
  mutate(iter = 1:n()) %>%
  pivot_longer(starts_with("r_targetWord")) %>%
  mutate(name = str_remove(name, pattern = "r_targetWord__logalpha"),
         name = str_remove(name, pattern = "\\,Intercept"),
         name = str_remove_all(name, pattern = "\\[|\\]"))%>%
  mutate(val = exp(b_logalpha_Intercept + value))%>%
  select(-b_logalpha_Intercept, -value)%>%
  mutate(nlpar = "Discrimination")%>%
  filter(val < 4)

params_joy <- bind_rows(eta_joy, alpha_joy) %>%
  rename(item = name)%>%
  left_join(aoa%>%rename(item = targetWord))

#saveRDS(params_joy, "../saves/model_params_irt3_draws.rds")

ggplot(params_joy, aes(y = reorder(item, -aoa_german_comb), x = val, fill = aoa_german_comb))+
  geom_density_ridges(size = 0.2,scale = 4, alpha = .5)+
  facet_grid(~nlpar, scales = "free_x")+
  labs(y = "Item")+
  scale_fill_viridis_c(name = "AoA")+
  theme_minimal()

params_joy%>%
  group_by(nlpar)%>%
  summarise(min = min(val), 
            max = max(val))
```
